### 2022-06-08 Submission/STS/Research_Notebook.tex
research notebook up to 6/8/2022

\newcommand{\workingDate}{\textsc{2022 $|$ January $|$ 01}}
\newcommand{\userName}{Tanish Tyagi}
\newcommand{\institution}{Massachusetts General Hospital/Harvard Medical School}
\usepackage{researchdiary_png}
\usepackage{url}

@@

A minor breakthrough was made when we went back to further examining the predictions of the models that Xiao and I trained on 3/9/2022. When the sequence equals the full note, both the predictions of the sequence model and full note model are the same as well as the probability, which actually makes a lot of sense since the attention weights and pooling layers are the same among others.

>>>>

\newcommand{\workingDate}{\textsc{\today}}
\newcommand{\userName}{Tanish Tyagi}
\newcommand{\institution}{Massachusetts General Hospital/Harvard Medical School}
\usepackage{researchdiary_png}
\usepackage{url}

@@

A minor breakthrough was made when we went back to further examining the predictions of the models that I trained on 3/9/2022. When the sequence equals the full note, both the predictions of the sequence model and full note model are the same as well as the probability, which actually makes a lot of sense since the attention weights and pooling layers are the same among others.

\section{June 6, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb}

Today was my first day doing full-time research at the lab since last summer, and it was a great feeling to finally get back into it! I used the ClinicalBERT training script I created to train the sequence level deep learning model and applied it to the current database of annotated sequences (around 4700). Future plans include to apply the ClinicalBERT model to a final dataset of around 6500 sequences so that it can become a great sequence level predictor. By improving the sequence level predictions, the logistic regression patient level predictor model will also become significantly improved.

\section{June 7, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb}

I encountered a weird error when running the optuna study that I had not seen before. The terminal said that said \texttt{CUDA error: device-side assert triggered. CUDA kernel errors might be asynchronously reported at some other API call,so the stacktrace below might be incorrect. For debugging consider passing CUDA\_LAUNCH\_BLOCKING=1.} This error really did not tell me much, so I asked my colleagues and they recommended checking the dataset to ensure there are no bugs and to run the script from the commmand line as a python file instead of a jupyter notebook while specifying the GPU ports to use.

None of the above fixes worked, but luckily I was able to find a fix which was to remove all the columns in my train, validation, and test sets except "text" and "labels" and restarting the kernel. This was quite a strange fix, but at the same time I was given a strange error. The model will finish training tomorrow.

\section{June 8, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/ClinicalBERT\_Training\_Script.ipynb} \\ and \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT\_Trial\_Analysis.ipynb}

The model finished training this morning. The best trial was trial 10: with 0.974 AUC and 0.897 ACC on the evalulation set. The hyperparameters that were varied throughout the study had the below values for trial 10:

\begin{itemize}
   \item adam epilson: 5.3157E-06
   \item early stopping patience: 3
   \item learning rate: 5.5703E-05
   \item num train epochs: 1
\end{itemize}

The AUC and ACC were not as good as the previous iteration of the model, which means that I will have to spend more time finding hyperparameters to tune. Some options for this include increasing the number of trials in the Optuna study from 20 to 40 (potentially), having the Optuna study maximize AUC instead of ACC, increasing the range of possible values for the learning rate, and finding other hyperparameters to include in the Optuna tuning process in addition to the four mentioned above.

To dig deeper, I performed an analysis of the hyperparameters values for each trial and the corresponding AUC and ACC.

\begin{figure}[ht!]
\centering
\includegraphics[width=10cm]{auc_trial.png}
\caption{AUC per Trial}
\end{figure}
